Performing graph-based clustering with rOpenScPCA

### 2025-01-13 analyses/hello-clusters/01_perform-evaluate-clustering.Rmd
swap in new rprojroot line so this runs in CI, and re-render notebooks

```{r base paths}
# The base path for the OpenScPCA repository
repository_base <- rprojroot::find_root(rprojroot::is_git_root)

@@

To begin, we'll read in the `SingleCellExperiment` (SCE) object.
We'll also establish a corresponding processed Seurat object from its raw counts that we'll use for some examples.

@@

To demonstrate this, we'll convert our SCE object to a Seurat using the function `rOpenScPCA::sce_to_seurat()`.
Then, we'll use a simple Seurat pipeline to obtain clusters.
<!-- TODO: We will want to reference this module for further documentation on this function: https://github.com/AlexsLemonade/OpenScPCA-analysis/issues/945 -->

>>>>

```{r base paths}
# The base path for the OpenScPCA repository
repository_base <- rprojroot::find_root(rprojroot::has_dir(".github"))

@@

To begin, we'll read in the `SingleCellExperiment` (SCE) object.

@@

To demonstrate this, we'll convert our SCE object to a Seurat using the function `rOpenScPCA::sce_to_seurat()`.
Then, we'll use a simple Seurat pipeline to obtain clusters.
